\begin{rubric}{Softwares and Webserver Developed}
\subrubric{Softwares / Tools (5)}
\entrys[]\textbf{miPyRNA} (\href{https://github.com/navduhan/mipyrna}{https://github.com/navduhan/mipyrna}): an automated python package for small RNA sequencing data analysis.
\entrys[]\textbf{SNVguru} (\href{https://github.com/usubioinfo/snvguru}{https://github.com/usubioinfo/snvguru}): an automated python package for single nucleotide variation (SNV) analysis.
\entrys[]\textbf{pySeqRNA} (\href{https://github.com/navduhan/pyseqrna}{https://github.com/navduhan/pyseqrna}): an automated python package for next-generation sequencing data analysis.
\entrys[]\textbf{MINpred} (\href{https://bioinfo.usu.edu/minpred/download/minpred.tar.gz }{https://bioinfo.usu.edu/minpred/download/minpred.tar.gz}): a standalone alignment-free deep learning based tool for nitrogen mineralization enzyme classification.
\entrys[]\textbf{deepNEC} (\href{https://navduhan@bitbucket.org/navduhan/deepnec.git }{https://navduhan@bitbucket.org/navduhan/deepnec.git}): a standalone alignment-free deep learning based tool for nitrogen metabolism enzyme classification.

\subrubric{Webserver / Databases (13)}
\entrys[]\textbf{HPInet} (\href{http://bioinfo.usu.edu/hpinet/} {http://bioinfo.usu.edu/hpinet/}): a Cereal crops and pathogen prote-protein interaction database. (accessed by $\approx$ 20 users)
\entrys[]\textbf{HuPoxNET} (\href{http://bioinfo.usu.edu/hupoxnet/} {http://bioinfo.usu.edu/hupoxnet/}): a database for Human-Monkeypox virus interactome. (accessed by $\approx$ 20 users)
\entrys[]\textbf{myDockDB} (\href{http://bioinfo.usu.edu/myDockDB/} {http://bioinfo.usu.edu/myDockDB/}): a Multiple Myeloma Proteins and Natural Compounds Docking WEB-resource. (accessed by $\approx$ 20 users)
\entrys[]\textbf{pySeqRNA} (\href{http://bioinfo.usu.edu/pyseqrna/} {http://bioinfo.usu.edu/pyseqrna/}): complete documentation website for pySeqRNA package. (accessed by $\approx$ 112 users)
\entrys[]\textbf{ranchSATdb} (\href{http://bioinfo.usu.edu/ranchSATdb/} {http://bioinfo.usu.edu/ranchSATdb/}): a database of ranch animals microsatellite markers ( accessed by $\approx$ 30 users)
\entrys[]\textbf{TritiKBdb} (\href{http://bioinfo.usu.edu/tritikbdb/} {http://bioinfo.usu.edu/tritikbdb/}): a Host-Pathogen interaction database for understanding Karnal Bunt disease infection mechanisms in Wheat. (accessed by $\approx$ 540 users)
\entrys[]\textbf{HuCoPIA} (\href{http://bioinfo.usu.edu/hucopia/} {http://bioinfo.usu.edu/hucopia/}): an Atlas of Human vs. SARS-CoV-2 interactome and the comparative analysis with other Coronaviridae family viruses. (accessed by $\approx$ 60 users)
\entrys[]\textbf{deepNEC} (\href{http://bioinfo.usu.edu/deepNEC/} {http://bioinfo.usu.edu/deepNEC/}): an integrated web server platform for the prediction of nitrogen metabolism-related enzymes using deep learning. (accessed by $\approx$ 700 users)
\entrys[]\textbf{deepHPI} (\href{http://bioinfo.usu.edu/deepHPI/} {http://bioinfo.usu.edu/deepHPI/}): a Deep Learning framework for the prediction of host-pathogen protein interactions and visualization. (accessed by $\approx$ 1.03K users)
\entrys[]\textbf{GreeningDB} (\href{http://bioinfo.usu.edu/GreeningDB/} {http://bioinfo.usu.edu/GreeningDB/}): a database of host-pathogen interactions and studying
comparatomics of citrus and citrus greening disease (HLB). (accessed by $\approx$ 828 users)
\entrys[]\textbf{covidTracker} (\href{http://bioinfo.usu.edu/covidTracker/} {http://bioinfo.usu.edu/covidTracker/}): a COVID 19 disease infection statistics tracker. (accessed by $\approx$ 8200 users)
\entrys[]\textbf{legumeSSRdb} (\href{http://bioinfo.usu.edu/legumeSSRdb/}{http://bioinfo.usu.edu/legumeSSRdb/}): a Legume species microsatellite markers database. (accessed by $\approx$ 712 users)
\entrys[]\textbf{citSATdb} (\href{http://bioinfo.usu.edu/citSATdb/} {http://bioinfo.usu.edu/citSATdb/}): a Citrus species microsatellite markers database. (accessed by $\approx$ 530 users)
\end{rubric}
    
